Numerical Investigation of the Accuracy, Stability, and Efficiency of Lattice Boltzmann Models in Simulating Non-Newtonian Flows

### 2016-07-07 main.tex
updated captions for noneq moment figures

\begin{figure}
    \includegraphics[width=\linewidth]{figs/poise-bingham/epsilon}
    \caption{Particle distributions in the 5 direction (left) and 8 direction (right) compared to their respective quasiequilibriums for the MRT with $m = 10^8$.}
    \label{fig:epsilon}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figs/poise-bingham/qx}
    \caption{Particle distributions in the 5 direction (left) and 8 direction (right) compared to their respective quasiequilibriums for the MRT with $m = 10^8$.}
    \label{fig:qx}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figs/poise-bingham/epsilon_cumulative}
    \caption{Particle distributions in the 5 direction (left) and 8 direction (right) compared to their respective quasiequilibriums for the MRT with $m = 10^8$.}
    \label{fig:epsilon-cumulative}
\end{figure}

\begin{figure}
    \includegraphics[width=\linewidth]{figs/poise-bingham/qx_cumulative}
    \caption{Particle distributions in the 5 direction (left) and 8 direction (right) compared to their respective quasiequilibriums for the MRT with $m = 10^8$.}
    \label{fig:qx-cumulative}
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=\linewidth]{figs/poise-bingham/epsilon}
    \caption{Evoluation of relative $L_2$, $\epsilon^{neq}$ with time. The norm of the $\epsilon^{neq}$ across the height of the channel is an indicator of an increase in oscillations at the lattice level due to the $\epsilon$ moment.}
    \label{fig:epsilon}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figs/poise-bingham/qx}
    \caption{Evoluation of relative $L_2$, $q_x^{neq}$ with time. The norm of the $q_x^{neq}$ across the height of the channel is an indicator of an increase in oscillations at the lattice level due to the $q_x$ moment.}
    \label{fig:qx}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figs/poise-bingham/epsilon_cumulative}
    \caption{Cumulative relative $L_2$, $\epsilon^{neq}$ with time. Oscillations can have a positive effect on each other, building up. The cumulative relative $L_2$, $\epsilon^{neq}$ is a measure of how much oscillations due to the $\epsilon$ moment may have been building in time.}
    \label{fig:epsilon-cumulative}
\end{figure}

\begin{figure}
    \includegraphics[width=\linewidth]{figs/poise-bingham/qx_cumulative}
    \caption{Cumulative relative $L_2$, $q_x^{neq}$ with time. Oscillations can have a positive effect on each other, building up. The cumulative relative $L_2$, $q_x^{neq}$ is a measure of how much oscillations due to the $q_x$ moment may have been building in time.}
    \label{fig:qx-cumulative}
\end{figure}
